The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd

# Unnest tokens and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word)) |>  # lemmatise words
  filter(nchar(word) >= 3)  # keep only words that are at least three letters long

>>>>

# Unnest tokens and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word)) |>  # lemmatise words
  filter(nchar(word) >= 3)  # keep only words that are at least three letters long
```
